\sysfull

### 2018-04-17 paper/coalescing.tex
some TODOs for oopsla18
last comments from OOPSLA 2018 branch by Alexei ported manually to main branch
heavy pass over coalescing

When incoming energy is sufficient to run multiple consecutive tasks,
committing state after each task is wasteful. \sys mitigates this
waste by deferring the expensive commits and performing them in a
batch. In the resulting execution, several tasks are \emph{merged} into a
single virtual task---a process we call \emph{coalescing}. 
%
When $N$ tasks are coalesced, $N-1$ boundaries are crossed and some number of
pages are dirtied. The first $N-2$ executions of \transition statement skip
committing dirty pages to non-volatile memory, leaving the work of committing
pages modified by any of the $N$ tasks to the statement $N-1$.
Coalescing is likely to reduce the total number of non-volatile memory
accesses, because when coalesced tasks access the same pages of data, only the
last version of the page needs to be committed.

\textbf{Trade-off between Speed and Wasted Effort.} \sys can coalesce an
arbitrary number of consecutive tasks. However, as more tasks coalesce, their
collective commit overhead amortizes better, but the risk of wasting work also
increases. If power fails during a long sequence of coalesced tasks, execution
will restart from the last commit, i.e. the first task in the sequence, losing
the progress made by any of the coalesced tasks.  The challenge to coalescing
tasks is determining how many tasks to coalesce before committing.
%
%During execution, an executing task is either a {\em coalesced} task, which
%does not commit its state before transitioning or a {\em committing} task,
%which does commit its state before transitioning.

\textbf{Task Coalescing Strategies.} 
%
The likelihood that a task group will complete depends on the total amount of
energy consumed by all tasks in the group, i.e. the size of the dynamic task.
%
A good coalescing strategy must moderate the risk of wasted work and capitalize
on benefits of deferred commits by adapting the target size of the dynamic task
to the energy available at runtime.
%
The general structure of our strategies is to increase the target task size by
some positive delta $C_\text{up}$ after the dynamic coalesced task completes,
and decrease it by some negative delta $C_\text{down}$ upon a reboot after a
power failure.
%
The choice of $C_\text{up}$ and $C_\text{down}$, including their units, defines
the strategy and its performance.
%
For example, a naive strategy that fixes $C_\text{up}$ and $C_\text{down}$ to
``one static task``, will be very slow to react to changes in incoming energy,
since its dynamic task size can only change by the size of one (small) static
task per charge-discharge cycle.
%
Working from these observations, we propose and evaluate two coalescing
strategies for \sys: \textbf{History-aware Coalescing (HC)} and
\textbf{Task-size- and History-aware Coalescing (TSHC)}.

%\begin{enumerate}
%	\item \textbf{Interrupt History Coalescing (HDC):} when more tasks are coalesced without power interrupt, $C_U$ increases, and $C_D$ increases, as more task are interrupted before committing; and 
%	\item \textbf{Weighted Interrupt History Coalescing (WHDC):} where coalescing strategy follows the one of HDC, while also taking into account the \emph{expected execution time} of each task in the application.
%\end{enumerate}

\subsection{HC: History-aware Coalescing}

\todo{clarify}{AC}
With this strategy \sys calculates only one parameter $C=C_\text{up}=C_\text{down}$ based on the number of tasks completed, until $t$th task commit, $S_t$, during the current operational period. \sys begins execution in a coalesced task with $S_t=0$. When $S_t=C_{t-1}-1$ coalesced tasks have been executed without power interrupt (where $C_{t-1}$ defines $C$ until $t-1$ task commit) a task commit follows. After each commit, \sys assigns new coalescing factor as $C_{t}=\lceil \sum_{k=1}^{t}S_{k-1}/2\rceil$. This implies that if more tasks complete in an operating period, \sys attempts to coalesce more tasks. However, tasks coalescing are increased by a half the speed of the successful task completion. This way we adapt to the coalescing speed/wasted effort trade-off: at the potential power interrupt \sys does not immediately reduce coalescing factor to one, and with successful page commit of coalescing task, \sys gradually increases coalescing factor. In both cases \sys reduces the effect of outliers, i.e. short bursts of energy or short bursts of frequent power interrupts.

%\textbf{Task Coalescing Illustration.} Figure~\ref{fig:coalescing_example_states} shows a sequence of three tasks executing in \sys. At left, there is no coalescing and tasks incur the cost of commit at each transition. The center shows the same tasks executing as coalesced groups of two tasks $C=2$, avoiding one commit. At right, \sys coalesces three tasks ($C=3$) avoiding two commits. Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value of $C$ based on $S$. \sys executes tasks in the first operating period, with $C$ equal to half the number of tasks completed in the prior execution period. In the example, $C$ starts at eight. After completing eight tasks, \sys commits and reduces $C$ by half to four. \sys completes two of four tasks and power fails.  During the operating period, \sys executed a total of ten tasks (i.e., $S=10$) and when \sys restarts, $C$ is assigned to five (i.e., half of $S$). \sys completes the five coalesced tasks $S=5$ and after committing, assigns $C$ to half of $S$, which is three (after rounding up). \sys coalesces three tasks and again commits.  At this point, $S=8$; \sys assigns $C=4$ and execution continues.

\subsection{TSHC: Task-size- and History-aware Coalescing}

The history-aware coalescing policy used the number of tasks in the group as a
rough proxy for the energy cost of the task group.
%
With some up-front investment of developer effort and modest time and space
overhead, a more precise proxy for task size can be obtained by profiling the
tasks at design time.
%
The TSHC policy approximates task energy cost from a profile of task execution
times.
%
Profiling execution time instead of direct energy consumption is
advantageous, because the former does not require specialized
current\hyp{}measurement hardware and can be readily done on any
off-the-shelf microcontroller.
%
To use the TSHC policy, the application is first profiled, as will be described
in the experiment below, and the task execution time for each task is written
into a read-only table in non-volatile memory.
%
At runtime, the decision to coalesce or commit at each task boundary proceeds
similarly with the HC policy, but the task completion counter, $S_t$ has units
of ``task execution time''.\todo{be precise}{AC}

To quantify the importance of task size in the coalescing decision, we measured
the distribution of task sizes in our benchmarks (described in
Sections~\ref{sec:results_software}).
%
Each benchmark was run for 10 seconds on non-intermittent power, and a timestamp
in clock cycles was taken at each task boundary. For each execution of
a task, its size was estimated as the maximum difference in timestamps at its
boundaries.
%
The CDF for the distribution of task sizes in Figure~\ref{fig:task_profiling}
shows the wide range of task sizes across and within benchmarks, and explains
the advantage of the TSHC policy.

%At the end of
%task measurement, normalized integer values of task execution for task $x$, $W_x$, are
%collected---the shortest one being one task, the longest one $W_{x,\max}$ (in
%case of Figure~\ref{fig:task_profiling} $W_{x,\max}=5$). Result of the task
%size measurement is provided in Figure~\ref{fig:task_profiling}.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/TskDist.pdf}%coalescing_timeline
	\caption{\textbf{Distribution of task sizes, estimated by task execution times.} The wide variation in task size motivates accounting for task size in the coalescing strategy.}
	\label{fig:task_profiling}
\end{figure}

%\begin{figure}
%	\centering
	%\subfloat[\sys coalesces consecutive tasks.]{\includegraphics[width=\columnwidth]{figures/coalescing_states}\label{fig:coalescing_example_states}}\\
	%\subfloat[\sys dynamically adapts the amount of coalescing.]{\includegraphics[width=\columnwidth]{figures/coalescing_timeline}\label{fig:coalescing_example_flowchart}}
	%\caption{\sys coalesces tasks to avoid overheads.}
	%\label{fig:coalescing_example}
%\end{figure}

%However, it takes a conservative approach by making the virtual task size equal
%to the half of the number of successfully executed real tasks before the last
%power interrupt (see lines~\ref{algo:coalescing:executionHistory1},
%\ref{algo:coalescing:executionHistory2} of Algorithm~\ref{algo:coalescing}). 
%
%We
%advocate for the algorithm conservative approach by the following two reasons:
%(i) the power interrupts are not uniformly distributed over the tasks; and (ii)
%the re-execution penalty, in case of a power interrupt, grows linearly with the
%size of a virtual task. 
%
%Furthermore, the algorithm considers the charging rate
%by allowing the real tasks counter (RTC), which represents the execution
%history between the last two power interrupts, to increase from one up to
%multiple virtual tasks (see line~\ref{algo:coalescing:realTaskCounter} of
%Algorithm~\ref{algo:coalescing}). 
%
%As a consequence, the virtual task size
%changes rapidly (since it is half of the execution history) in response to the
%change in the charging rate. 
%
%However, the algorithm sets a limit to the size of
%the virtual task for these two reasons: (i) having an infinity virtual task
%size, results in a certain computation progress loss; and (ii) the benefit of
%task merging is governed by the diminishing return principle (which will be
%demonstrated experimentally in Section~\ref{sec:results_coalescing}).
%
%The algorithm protects itself from power interrupts by going into three stages:
%(i) virtual progressing, where the operations are done on the volatile memory
%(see
%lines~\ref{algo:coalescing:virtualProgressing1}--\ref{algo:coalescing:virtualProgressing2}
%of Algorithm~\ref{algo:coalescing} ); 
%(ii) transition stage, where the volatile
%state is moved to a temporary persistent buffer. 
%
%Until the end of the second
%stage if a power is interrupted, then all the virtual progress will be
%cancelled and the virtual task will re-executed and re-initialized from a
%consistent input (see line~\ref{algo:coalescing:virtualProgressing1} of
%Algorithm~\ref{algo:coalescing}); 
%
%and (iii) persistent commit stage, upon
%entering this stage the algorithm will make a firm transition (see
%lines~\ref{algo:coalescing:firmTransition1},
%\ref{algo:coalescing:firmTransition2} of Algorithm~\ref{algo:coalescing}) and
%it will not go back to the other stages unless all the data is committed from
%the persistent buffer to non-volatile memory. 
%
%Since the data is being moved in one direction and from a persistent location,
%power interrupt is tolerable at this stage.

%\begin{algorithm}[t]
%	\caption{\sys task coalescing mechanism}
%	\label{algo:coalescing}
%	\scriptsize
%	\begin{algorithmic}[1]
%		\State $\text{p}$  \Comment{Indicates persistent variables, initialized \textbf{only} during device programming}
%		\State $\text{RT} \in \{\sys~\text{static tasks}\}$  \Comment{Real task}
%		\State $\text{VT} \subset \{~\text{RT's}\}$  \Comment{Virtual task}
%		\State $\text{RTC}$  \Comment{RT counter}
%		\State $\text{VTC}$  \Comment{VT counter}
%		% \State $|\text{VT}|$ \Comment{VT size measured in RT}
%		\State $\text{TVT}$ \Comment{Temporary VT}
%		\State $\text{VT}_{\max}$ \Comment{Maximum VT size measured in RT (coalescing upper bound)}
%		\vspace{0.1cm}
%		
%		\State $\text{p RTC} = x $ 
%		\State $\text{p VT}_{\max} = y$
%		\State $\text{p VT} = \text{RT}$ 
%		\State $\text{p TVT} = \text{VT} $ 
%		\State $\text{VTC} = 0 $ 
%		\vspace{0.1cm}
%
%		\Function{scheduler}{\null}
%
%			\State $\text{VTC} = \text{RTC/2} $  \label{algo:coalescing:executionHistory1}
%			\State $\text{RTC} = 0 $
%			\State $\text{RT} = \text{VT}$ \Comment{Recover virtual state} \label{algo:coalescing:virtualProgressing1}
%			\If{commiting}
%				\State $\text{RT}=\text{TVT}$
%				\State $\texttt{goto} \ \ \ref{commitStage}$ \label{algo:coalescing:firmTransition1}
%			\EndIf
%			\vspace{0.1cm}
%
%			\While {True}
%				\While{$\text{VTC}--$}
%					\Function{execute}{$\text{RT}$}
%					\EndFunction
%					\If{$\text{RTC} < \text{VT}_{\max}$}
%						\State $\text{RTC}++$  \label{algo:coalescing:realTaskCounter}
%					\EndIf
%					\State $\text{RT} \leftarrow \text{RT}_{next}$ \Comment{Virtual progressing}
%				\EndWhile        \label{algo:coalescing:virtualProgressing2}
%
%				\State \Comment{Virtual task is finished}
%				\State $\text{Data} \rightarrow \text{pTempBuf}$ \Comment{pTempBuf: persistent temporary buffer}
%				\State $\text{TVT} = \text{RT}$ 
%				\State $\text{commiting} = \text{True}$ \label{algo:coalescing:firmTransition2}
%				\State 
%				\State $\text{VT} = \text{TVT}$ \label{commitStage}
%				\State $\text{pTempBuf} \rightarrow \text{FRAM}$ 
%				\State $\text{VTC} = \text{RTC/2}$ 		\Comment{Set VT size} \label{algo:coalescing:executionHistory2}
%				\State $\text{commiting} = \text{False}$ 
%
%			\EndWhile
%
%		\EndFunction
%			
%	\end{algorithmic}
%\end{algorithm}

%\subsection{Power Interrupt Immune Scheduler}
%
%\input{relativeJumpAlgo.tex} %Task jumping algorithm
%
%It utilizes a persistent circular buffer (i.e. persistent linked list) to keep the state of a program across power failures. \sys provides an API to enable a programmer to have a full control over the execution flow of the program, i.e. (un)blocking a task or re-execute the same task which is particularly important in the intermittent execution to emulate a persistent loop. \todo{Expand this section}{Amjad}
%
%\begin{algorithm}
%	\caption{Opportunistic virtual Task size}
%	\label{algo:fixVirtTask}
%	\scriptsize
%	%\small
%	\begin{algorithmic}[1]
%		\State $VT \subset \text{\{\sys Tasks\}} $  \Comment{$VT:$ Virtual Task}
%		\State VTS : VT size
%		\vspace{0.1cm}
%		
%		\While {$True$}
%		\State $VT \leftarrow VT_{next}$
%		\vspace{0.1cm}
%		\While {execute $VT$} 
%		\If { $\text{power failed twice}$ }				
%		\State $VTS--$  
%		\EndIf
%		\EndWhile
%		
%		\vspace{0.1cm}
%		\If {$ \text{All tasks executed}$}
%		\State $VTS++$
%		\EndIf
%		\EndWhile
%	\end{algorithmic}
%\end{algorithm}

>>>>

\sys's design includes a novel task scheduler that uses efficient,
energy-aware task coalescing to amortize task overheads, and uses a timer-based
task-splitting mechanism to avoid non-termination of tasks too long
for a device's energy buffer.

\subsection{Task Coalescing}
\label{sec:task_coalescing}

% \begin{wrapfigure}{t!}{0.5\textwidth}
% 	\centering
% 	\includegraphics[width=0.5\columnwidth]{figures/coal_Intro_Figure.pdf}
% 	\caption{When $N$ tasks coalesced $N-1$ commit operations are skipped.}
% 	\label{fig:coalIntro}
% \end{wrapfigure}

When a device's buffered energy is sufficient to run multiple consecutive tasks
without a power failure, committing state after each task is an unnecessary
overhead.   \sys eliminates this overhead by {\em coalescing} a sequence of
consecutive tasks. \sys coalesces a sequence of tasks by deferring the commit
operations for all tasks to the end of the sequence, performing their commits
as a batch.  In general, committing involves moving state manipulated by a task
into its permanent location in non-volatile main memory.  In particular, \sys's
commit procedure copies dirty pages of memory that a task updated between fast,
volatile working memory and slower, non-volatile main memory; we defer the
details of paging and commit to Section~\ref{sec:memory_virtualization}.

When \sys coalesces a sequence of $N$ tasks, \sys avoids the cost of commit at
the first $N-1$ boundaries.   The first $N-1$ inter-task transitions leave
dirty pages in working memory, deferring the work of committing dirty modified
until the commit of the last task in the sequence.  Coalescing tasks brings a
double benefit. First, coalescing reduces the total number of relatively
high-latency, high-energy non-volatile memory accesses because tasks primarily
access variables in relatively low-latency, low-energy volatile memory.
Second, coalescing eliminates the unnecessary instructions that implement task
commit, which our measurements in Section~\ref{sec:evaluation} show constitute
a substantial run-time overhead.

%it fasten applicaiton exeution be skipping unnecessary data commits operations
%when there is abandond energy.

The effectiveness of coalescing tasks hinges on having an effective {\em
coalescing strategy}, which determines how many consecutive tasks to coalesce.
An effective strategy must be {\em aggressive} enough, attempting to coalesce a
large number of consecutive tasks to amortize a large amount of commit overhead.   
%
If power fails during a long sequence of coalesced tasks, execution will
restart from the last commit, i.e. the first task in the sequence, losing the
progress made by any of the coalesced tasks.
%
An effective strategy must also be {\em
conservative} enough, attempting to coalesce only as many tasks as will execute
to completion using the device's available energy, but no more.
%
An effective coalescing strategy moderates the risk of a power failure during a
long coalesced task and capitalizes on the benefits of deferred commits by
adapting the target size of the dynamic task to the energy available at
runtime.

%\textcolor{red}{maybe is possible to demonstrate with data? count number of executed non-volatile vs volatile accesses}
%

\noindent \textbf{Task Coalescing Strategies.} 
% % Carlo pseudo code 
% \begin{algorithm}[t]
% 	\caption{Coalescing}
% 	\label{algo:genCoalescing}
% 	\scriptsize
% 	%\small
% 	\begin{algorithmic}[1]
%         \State $H_\text{p} \gets H_\text{c}$
%         \State $H_\text{p} \gets 0$ 
%         \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$B, H_\text{p}$}

%         \While{$\texttt{true}$}
% 	        \State $ B_\text{c} \gets B$
% 	        %
% 	        \While{$ B_\text{c} > 0$}
% 		        \State \Call{execute\_task}{$T_\texttt{i}$}
% 		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
% 		        \State $B_\text{c} \gets B_\text{c} - W$
% 				\State $H_\text{c} \gets H_\text{c} + W$
% 	        \EndWhile
% 	        %
% 	         \State $B \leftarrow $ \Call{$f_\text{compl}$}{B, $H_\text{c}$,$H_\text{p}$}
% 	        \State \Call{commit\_to\_fram}{\null}
%         \EndWhile
% 	\end{algorithmic}
% \end{algorithm}
% %
% To describe the proposed strategies we will use the following parameters:
% \begin{itemize}
% \item target budget $B$: total number of static tasks to be coalesced.
% \item current budget $B_\text{c}$: remaining number of tasks to be coalesced before committing to non-volatile memory; 
% \item history $H$: up on reboot, it is the number of executed static tasks between the last two power interrupts. While executing, it is the number of executed static tasks since the last power interrupt.
% \end{itemize}
%
%
% Modifiying Carlo's pseudo code a little 
\begin{algorithm}[t]
	\caption{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$H$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}
\end{algorithm}
%
%
Algorithm~\ref{algo:genCoalescing} shows the general structure of a coalescing
strategy. In the algorithm, $B$ (target budget) is total number of static tasks
that \sys will next attempt to coalesce. $T_\text{i}$ is the $i^{th}$ task
executed since the last power failure. $H$ (history) is the number tasks
(coalesced or not) executed between the two most recent power failures.
$W_\text{i}$ is the {\em weight} of a task $T_\text{i}$.  A task's weight is an
arbitrary quantity associated with the task that represents its cost in time or
energy to execute; different coalescing strategies may apply different weights
to a task.  For example, a uniform weighting scheme sets the weight of each
task to one, making them all effectively equal in cost to the coalescing
algorithm.  A different policy might use a weighting scheme that sets a task's
weight equal to its run time relative to the task that executes for the
shortest duration, which has unity weight.

Different coalescing strategies adhere mainly to the template in
Algorithm~\ref{algo:genCoalescing}, varying in only a few {\em characteristic
operations} that the algorithm leaves deliberately abstract.  A strategy's
reboot update function, $f_\text{reboot}$, updates $B$, the target budget,
after a reboot. A strategy's weight lookup function, $f_\text{weight}$, returns
the a task's weight.  A strategy's commit update function, $f_\text{commit}$,
updates $B$ after a successful commit. The following sections detail several
possible coalescing strategies that we developed for \sys.

\subsubsection{Energy-oblivious Coalescing (EB)}
\label{subsec:energyBlind}

\begin{wrapfigure}{t!}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/slowCoal}
	\caption{The {\em energy-oblivious coalescing} algorithm \emph{linearly} updates its coalescing target.}
	\label{fig:energyBlind}
\end{wrapfigure}

A very simple {\em energy-oblivious} coalescing strategy treats all tasks as
having unity weight and varies the size of a coalesced task linearly. In such a
scheme, the number of tasks to coalesce, $B$, increases by a constant $x$ when
a coalesced sequence of tasks commits, and decreases by the same constant $x$
when a coalesced sequence of tasks fails to complete (i.e., after a power
failure).  The characteristic operations of the energy-oblivious strategy are:

\begin{itemize}
\item $f_\text{reboot}(B) = B - x $;
\item $f_\text{weight}(T_\text{i}) =  1$; 
\item $f_\text{commit}(B) = B + x$; 
\end{itemize}

The energy-oblivious strategy reacts slowly to the variation in the energy
required to execute different tasks and to the in the effective quantum of
energy available to the device (i.e., variation in energy buffer size). 
%
Figure~\ref{fig:energyBlind} shows how this strategy may experience a 
large number of repeated power failures without forward progress.
%
With the successful commit of each coalesced task sequence, the coalescing
target increases.  Eventually, the target may be too high and a coalesced task
composed of only fewer tasks will commit without interruption by a power
failure.
%
The strategy then slowly decreases the coalescing target, eventually reaching a
coalescing target that allows completion.
%

A key limitation of this algorithm lies in the equality of the target decrease
in $f_\text{reboot}(B)$ and the increase in $f_\text{reboot}(B)$.  If, after
some number $k$ successful commits the target must decrease back to its
original value before the $k$ commits, the algorithm must then decrease $B$ by
$k \times x$.  To accumulate this decrease, this strategy requires $k$ power
failures, after each of which the strategy decreases $B$ by $x$, eventually
decreasing by $k \times x$, but only after a long time.

\subsubsection{History-Guided Coalescing (HG)}
\label{subsec:energyAware}
The History-Guided (HG) coalescing strategy adapts the coalescing target more
quickly, addressing a key limitation of the EB coalescing strategy.  
%
EA gives each task unity weight, as with EB.  
%
HG differs from EB in how it updates $B$ on commit, and after a power failure.
%
HG assumes that as the duration of execution since a power failure increases,
the amount of energy remaining decreases, and the risk of failing during a long
sequence of coalesced tasks increases.  
%
Consequently, HG decreases the coalescing target by half with each successful commit.
%
HG is {\em history-guided} because it initializes the coalescing target to be
equal to $H$, the total number of tasks executed between the most recent pair
of power failures.
%
While a history of $H$ suggests that there is sufficient energy to coalesce and
successfully commit $H$ tasks (i.e., to set $B = H$), HG conservatively sets $B$ equal to half
of $H$ moderating the risk of a very long coalesced task. 
%
The fraction of the history by which HG adjusts $B$ is arbitrary.
We experimented with a range of fraction values, settling on one half as the
default for HG, because one half had the highest performance.

The EA algorithm is characterized by the following functions:

\begin{itemize}
\item $f_\text{reboot}(B) = \lfloor(H / 2)\rfloor;$
\item $f_\text{weight}(T_\text{i}) =  1$; 
\item $f_\text{commit}(B) = \lfloor(B / 2)\rfloor;$ 
\end{itemize}

Figure~\ref{fig:energyAware} illustrates the operation of the history-guided
coalescing strategy.  Each white box is a task and each red box is a commit.
Time goes left to right and consecutive white boxes with no intervening commit
are coalesced tasks.  A gray box is a task interrupted by a power failure.  At
the top, the figure shows the $i^{th}$ execution period, which has a history
value of $H^{(i)} = 6$.  $B$ is initially three and decreases to one.  Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the decrease in the coalescing target.  After the power failure, HG
first updates the history $H = H^{i+1} = 8$.  HG then uses the value of $H$ to
update $B$, setting $B$ equal to four and continuing execution.

\begin{wrapfigure}{}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/energy-aware-coal.pdf}
	\caption{placeholder}
	\label{fig:energyAware}
\end{wrapfigure}

%, without losing generality or requiring hardware support,
%Moreover, it takes advantage of the guarantees that the energy buffer offers on a fresh start by coalescing many static tasks.

\subsubsection{Weighted History-Guided Coalescing (WHG)}
\label{subsec:energyTaskAware}

The Weighted History-Guided (WHG) coalescing strategy accounts for the
different energy and time cost of a program's tasks when setting the coalescing
target.
%
Each different task in the program consumes a different amount of energy to
execute to completion.  
%
The EB and HG coalescing strategies assume each task has uniform energy cost:
for these strategies, $B$ simply corresponds to a target {\em count} of tasks
coalesced, regardless of the individual cost of each task.
%
However, if one task executes for ten seconds and another executes for one
second, counting tasks misjudges the amount of {\em work} in the coalesced
tasks.

Instead, WHG associates a non-unity weight with each task in the program. 
%
WHG tracks the sum of the weights of tasks in a coalesced sequence of tasks.
%
When the sum of weights reaches $B$, the target, WHG commits the coalesced
task.
%
WHG differs extends EB and HG to explicitly account for the variation in energy
cost of a program's tasks, eliminating the assumption that all tasks do the
same work, which is a key limitation.
%
WHG has the same characteristic operations as HG, except that
$f_\text{weight}(T_\text{i}) = W_\text{i}$.

The effectiveness of the WHG algorithm hinges on correctly identifying the
weight of each task, which WHG assumes is {\em statically} available.
%
Profiling the time and energy cost of tasks in a program is a difficult,
orthogonal problem~\cite{cleancut,baghsorkhi_cgo_2018}.
%
WHG could use the result of an arbitrarily sophisticated profiling procedure.
%
To produce a concrete result in this paper, we give WHG access to a simple
profile of task run time collected offline using a single fixed input.
%
WHG stores the profile in a lookup table that maps a task's identifier to its
weight, making the information available to \sys's scheduler at run time.
